Characterization of gaps in directly bonded Si compound optics

### 2014-10-22 AO_bondedSi.tex
closes #18- delete figure 6 altogether- figure 6 was VG03 cartoon of petal pattern

\begin{figure}[htbp]
\centerline{\includegraphics[width=0.95\columnwidth]{figs/VG03patternSchematic.pdf}}
\caption{Schematic of part VG03 \label{figVG03pattern}.  The 100 mm diameter VG03 is comprised of two 3.3 mm thick silicon pucks.  We patterned a 25 mm diameter hole on one of the pucks.  The depth was 4.0 $\mu$m as indicated by Dektak profilometry.  We also patterned a low-fill factor petal pattern surrounding the hole.  The purpose for these patterns was to have gaps of known dimensions against which we could test the optical metrology technique we describe in this paper.}
\end{figure}

@@

The three important characteristics of the gaps are their axial extent, their lateral areal extent, and their areal fill factor.  We bored holes in silicon with inductively coupled plasma etching.  We used two different gases with low and high etch rates.  CHF$_3$ on Si exhibited about 0.3 nm/second etch rate, SF$_6$ exhibited about 1 micron/minute.  The area exposed to the process gases was about 1 inch diameter circles, or 15 mm $\times$ 20 mm rectangles.  We protected the unexposed areas with thick photoresist.  We achieved etch depths of 15$\pm$5 nm and 4000$\pm$100 nm, as measured with Veeco NT9100 Optical Profiler for the small depth, and Dektak stylus profilometry for the large depth.  Table \ref{tabbondexper} has more information about the bonding samples, and Table \ref{tabPatternFills} lists the properties of the patterns.  The fill factor is defined as the pattern area covered by gaps relative to the total pattern area.  Figure \ref{figVG03pattern} shows a schematic of VG03 and its pattern, as described in Table \ref{tabbondexper}.  In a second round of experiments we achieved gap sizes of 14$-$95 nm on four substrates with three meshes with coarse, medium, and fine boxes, each with 50\% fill factors.  For measurements taken with the Veeco NT9100 Optical Profiler, uncertainties were constructed by inspecting the histogram of topology, as shown in Figure \ref{figVS20pattern}.  The large-scale distortions were removed from the topology by masking and flattening to ensure that the uncertainties accurately reflect the distribution of measured heights.  The stylus profiliometry measured values were simply assigned an uncertainty of 5\%, which was consistent with our intuition and experience.  Table \ref{tabbondexper} lists part numbers and descriptions for our bonded substrates.

@@

\begin{table}[h!]
\caption{UTexas Si bonding experiments \label{tabbondexper}}
\begin{center}
    \begin{tabular}{ c c c c c c}
    \hline
    Name & Diameter & Thickness & Pattern Type & Pattern Depth & Notes \\ 
    -  & mm & mm & - & nm & - \\ 
        \hline
    HA1     & 75   & $10$ $\times$ 2& None & - & \\
    VG01   & 100 &$1$ $\times$ 2 & None  & - &  \\
    VG02   & 100 & $3.3$ $\times$ 2 &  None  & - &  \\
    VG03   & 100 & $3.3$ $\times$ 2 &  Hole \&Petal & 4000$\pm$200 & See Fig. \ref{figVG03pattern}\\    
    VG04   & 100 & $1$ $\times$ 2 &  Patchwork Islands & 15$\pm7$ & \\
    VG07   & 100 & $1$ $\times$ 2 &  mesh C, M, F & 12$\pm7$ & \\ %see email from Victor on 5/16/13
    VG08   & 100 & $1$ $\times$ 2 &  mesh C, M, F & 12$\pm7$ & \\ 
    VG09   & 75   & $1$ $\times$ 2 & mesh C & 49 $\pm$6 & \\
    VG15   & 100 & $0.8$ $\times$ 2 &  mesh C, M, F  &14 $\pm$2 & \\
    VS20   & 100 & $0.8$ $\times$ 2 &  mesh C, M, F & 95 $\pm$5 & See Fig. \ref{figVS20pattern}\\
    \hline
    \end{tabular}
\end{center}
\end{table}

\begin{table}[h!]
\caption{Patterned gap properties \label{tabPatternFills}}
\begin{center}
    \begin{tabular}{ c c c c }
    \hline
    Pattern name & fill factor & minimum feature size & bulk description \\ 
    - & \% & $\mu$m & - \\ 
    \hline
    Hole & 100 & - & 25 mm diameter hole \\     
    Petal & $\sim1$ & $\sim$2000 & long petal lines, Fig. \ref{figVG03pattern} \\         
    Mesh F & 50 & 40 &  100 $\mu$m square holes, Fig. \ref{figVS20pattern}\\ 
    Mesh M & 50 & 200 &  500 $\mu$m square holes\\ 
    Mesh C & 50 & 620 &  1500 $\mu$m square holes\\     
        \hline
    \end{tabular}
\end{center}
\end{table}

>>>>

@@

The three important characteristics of the gaps are their axial extent, their lateral areal extent, and their areal fill factor.  We bored holes in silicon with inductively coupled plasma etching.  We used two different gases with low and high etch rates.  CHF$_3$ on Si exhibited about 0.3 nm/second etch rate, SF$_6$ exhibited about 1 micron/minute.  The area exposed to the process gases was about 1 inch diameter circles, or 15 mm $\times$ 20 mm rectangles.  We protected the unexposed areas with thick photoresist.  We achieved etch depths of 15$\pm$5 nm and 4000$\pm$100 nm, as measured with Veeco NT9100 Optical Profiler for the small depth, and Dektak stylus profilometry for the large depth.  Table \ref{tabbondexper} has more information about the bonding samples, and Table \ref{tabPatternFills} lists the properties of the patterns.  The fill factor is defined as the pattern area covered by gaps relative to the total pattern area.  In a second round of experiments we achieved gap sizes of 14$-$95 nm on four substrates with three meshes with coarse, medium, and fine boxes, each with 50\% fill factors.  For measurements taken with the Veeco NT9100 Optical Profiler, uncertainties were constructed by inspecting the histogram of topology, as shown in Figure \ref{figVS20pattern}.  The large-scale distortions were removed from the topology by masking and flattening to ensure that the uncertainties accurately reflect the distribution of measured heights.  The stylus profiliometry measured values were simply assigned an uncertainty of 5\%, which was consistent with our intuition and experience.  Table \ref{tabbondexper} lists part numbers and descriptions for our bonded substrates.

@@

\begin{table}[h!]
\caption{UTexas Si bonding experiments \label{tabbondexper}}
\begin{center}
    \begin{tabular}{ c c c c c c}
    \hline
    Name & Diameter & Thickness & Pattern Type & Pattern Depth & Notes \\ 
    -  & mm & mm & - & nm & - \\ 
        \hline
    HA1     & 75   & $10$ $\times$ 2& None & - & \\
    VG01   & 100 &$1$ $\times$ 2 & None  & - &  \\
    VG02   & 100 & $3.3$ $\times$ 2 &  None  & - &  \\
    VG03   & 100 & $3.3$ $\times$ 2 &  Hole \&Petal & 4000$\pm$200 & \\    
    VG04   & 100 & $1$ $\times$ 2 &  Patchwork Islands & 15$\pm7$ & \\
    VG07   & 100 & $1$ $\times$ 2 &  mesh C, M, F & 12$\pm7$ & \\ %see email from Victor on 5/16/13
    VG08   & 100 & $1$ $\times$ 2 &  mesh C, M, F & 12$\pm7$ & \\ 
    VG09   & 75   & $1$ $\times$ 2 & mesh C & 49 $\pm$6 & \\
    VG15   & 100 & $0.8$ $\times$ 2 &  mesh C, M, F  &14 $\pm$2 & \\
    VS20   & 100 & $0.8$ $\times$ 2 &  mesh C, M, F & 95 $\pm$5 & See Fig. \ref{figVS20pattern}\\
    \hline
    \end{tabular}
\end{center}
\end{table}

\begin{table}[h!]
\caption{Patterned gap properties \label{tabPatternFills}}
\begin{center}
    \begin{tabular}{ c c c c }
    \hline
    Pattern name & fill factor & minimum feature size & bulk description \\ 
    - & \% & $\mu$m & - \\ 
    \hline
    Hole & 100 & - & 25 mm diameter hole \\     
    Petal & $\sim1$ & $\sim$2000 & long petal lines \\         
    Mesh F & 50 & 40 &  100 $\mu$m square holes, Fig. \ref{figVS20pattern}\\ 
    Mesh M & 50 & 200 &  500 $\mu$m square holes\\ 
    Mesh C & 50 & 620 &  1500 $\mu$m square holes\\     
        \hline
    \end{tabular}
\end{center}
\end{table}
